Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-02-27 paper/EDA.qmd
Summary tables for qualitative and quantitative variables

```{r}
#| echo: true
#| message: false
#| warning: false
#| results: asis

# Compute summary statistics individually
m1_game_before <- mean(clean_data$game_before, na.rm = TRUE)
m2_game_before <- median(clean_data$game_before, na.rm = TRUE)
m3_game_before <- sd(clean_data$game_before, na.rm = TRUE)
m4_game_before <- IQR(clean_data$game_before, na.rm = TRUE)

@@

# Ensure the table prints correctly
print(summary_table)

# Display formatted table using kable
kable(summary_table, 
      caption = "Summary Statistics for Quantitative Variables",
      align = "c") |> print()
```

@@

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false

# References:
# https://tellingstorieswithdata.com/
# https://q.utoronto.ca/courses/376099/pages/project-descriptions?module_item_id=6379323

library(kableExtra)

m1_game_before <- mean(clean_data$game_before, na.rm = TRUE)
m2_game_before <- median(clean_data$game_before, na.rm = TRUE)
m3_game_before <- sd(clean_data$game_before, na.rm = TRUE)
m4_game_before <- IQR(clean_data$game_before, na.rm = TRUE)

@@

kable(summary_table, format = "latex", booktabs = TRUE, caption = "Summary Statistics for Quantitative Variables") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false

# Count and percentage for Drug
drug_counts <- table(clean_data$drug)
drug_percentages <- prop.table(drug_counts) * 100
drug_summary <- data.frame(Drug = names(drug_counts), Count = as.numeric(drug_counts), Percentage = round(drug_percentages, 2))

# Count and percentage for Dosage Level
dosage_counts <- table(clean_data$dosage_level)
dosage_percentages <- prop.table(dosage_counts) * 100
dosage_summary <- data.frame(Dosage = names(dosage_counts), Count = as.numeric(dosage_counts), Percentage = round(dosage_percentages, 2))

# Count and percentage for Location
location_counts <- table(clean_data$location)
location_percentages <- prop.table(location_counts) * 100
location_summary <- data.frame(Location = names(location_counts), Count = as.numeric(location_counts), Percentage = round(location_percentages, 2))

# Count and percentage for Age Group
age_counts <- table(clean_data$age_group)
age_percentages <- prop.table(age_counts) * 100
age_summary <- data.frame(Age_Group = names(age_counts), Count = as.numeric(age_counts), Percentage = round(age_percentages, 2))

kable(drug_summary, format = "latex", booktabs = TRUE, caption = "Summary of Drug Types") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

kable(dosage_summary, format = "latex", booktabs = TRUE, caption = "Summary of Dosage Levels") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

kable(location_summary, format = "latex", booktabs = TRUE, caption = "Summary of Locations") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

kable(age_summary, format = "latex", booktabs = TRUE, caption = "Summary of Age Groups") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
